---
title: "Probability"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---


5.  How does Kobe Bryant's distribution of streak lengths compare to the distribution 
of streak lengths for the simulated shooter? Using this comparison, do you have 
evidence that the hot hand model fits Kobe's shooting patterns?
<strong> Answer Question 5 to the left.</strong>

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```

We can then take a look at the distribution of these streak lengths.

## Simulating the Independent Shooter

Simulating a basketball player who has independent shots uses the same mechanism 
that we use to simulate a coin flip. To simulate a single shot from an 
independent shooter with a shooting percentage of 50% we type,

To make a valid comparison between Kobe and our simulated independent shooter, 
we need to align both their shooting percentage and the number of attempted shots.

```{r calc-streak-kobe}
kobe_streak <- calc_streak(kobe_basket$shot)
```

```{r plot-streak-kobe}
ggplot(data = kobe_streak, aes(x = length)) +
  geom_histogram(binwidth = 1)
```

```{r sim-basket}
shot_outcomes <- c("H", "M")
sim_basket <- sample(shot_outcomes, size = 1, replace = TRUE)
```

```{r}
sim_basket <- sample(shot_outcomes, size = 133, replace = TRUE,
                     prob = c(0.45, 0.55))
```

```{r sim-streak-lengths}
sim_streak <- calc_streak(sim_basket)
```

```{r plot-sim-streaks}
ggplot(data = sim_streak, aes(x = length)) +
  geom_histogram(binwidth = 1)
```

<div id="exercise">
**Exercise**: What concepts from the course videos are covered in this lab? What 
concepts, if any, are not covered in the videos? Have you seen these concepts 
elsewhere, e.g. textbook, previous labs, or practice problems?
</div>

<div id="license">
This is a derivative of an [OpenIntro](https://www.openintro.org/stat/labs.php) lab, and is released under a [Attribution-NonCommercial-ShareAlike 3.0 United States](https://creativecommons.org/licenses/by-nc-sa/3.0/us/) license.
</div>