---
title: 'Lab 1 - Intro to probability and data'
description: 'Questions for Lab 1'
free_preview: true
---

## Question 1

```yaml
type: ExplorableExercise
key: 02d4222b54
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file:</strong>

```Type 'go()' and hit Enter to get started!```

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q1. How many variables are included in this data set?</strong>

`@possible_answers`
- 2
- 3
- 4
- 82
- 1710

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex1.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex1.init.R
# lab1_ex1.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex1.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Great work!"
msg3 <- "Keep trying!"
msg4 <- "Nope."
msg5 <- "Not quite."
ex() %>% check_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

---

## Question 2

```yaml
type: ExplorableExercise
key: 5440b387f2
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q2. What command would you use to extract just the counts of girls born?</strong>

`@possible_answers`
- `arbuthnot$boys`
- `arbuthnot$girls`
- `girls`
- `arbuthnot[girls]`
- `$girls`

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex2.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex2.init.R
# lab1_ex2.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex2.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Not quite."
msg2 <- "Nice job!"
msg3 <- "Keep trying!"
msg4 <- "Nope!"
msg5 <- "Try again!"

ex() %>% check_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

---

## Question 3

```yaml
type: ExplorableExercise
key: eb6689ed9c
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q3. Which of the following best describes the number of girls baptised over the years included in this dataset?

`@possible_answers`
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised.
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases.
- The number of girls baptised has decreased over time.
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point.

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex3.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex3.init.R
# lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex3.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again."
msg5 <- "Try again."

ex() %>% check_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

---

## Question 4

```yaml
type: ExplorableExercise
key: e64497e7f4
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q4. How many variables are included in this data set?</strong>

`@possible_answers`
- 2
- 3
- 4
- 74
- 2013

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex4.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex4.init.R
# lab1_ex4.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex4.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "You got it!"
msg3 <- "Keep trying!"
msg4 <- "Try again."
msg5 <- "Try again."

ex() %>% check_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

---

## Question 5

```yaml
type: ExplorableExercise
key: b073c8a4d3
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q5. Has the proportion of boys born in the US has decreased over time.

`@possible_answers`
- TRUE
- FALSE

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex5.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex5.init.R
# lab1_ex5.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex5.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "That's right!"
msg2 <- "Try again."

ex() %>% check_mc(1, feedback_msgs = c(msg1, msg2))
```

---

## Question 6

```yaml
type: ExplorableExercise
key: 8aee5ae535
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q6. Which of the following statements is true?</strong>

`@possible_answers`
- Every year there are more girls born than boys.
- Every year there are more boys born than girls.
- Half of the years there are more boys born, and the other half more girls born.

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex6.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex6.init.R
# lab1_ex6.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex6.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Great work!"
msg3 <- "Keep trying!"
ex() %>% check_mc(2, feedback_msgs = c(msg1, msg2, msg3))
```

---

## Question 7

```yaml
type: ExplorableExercise
key: 63abfd6950
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q7. Which of the following best describes the trend?</strong>

`@possible_answers`
- There appears to be no trend in the boy-to-girl ratio from 1940 to 2013.
- There is initially an increase in boy-to-girl ratio, which peaks around 1960. After 1960 there is a decrease in the boy-to-girl ratio, but the number begins to increase in the mid 1970s.
- There is initially a decrease in the boy-to-girl ratio, and then an increase between 1960 and 1970, followed by a decrease.
- The boy-to-girl ratio has increased over time.
- There is an initial decrease in the boy-to-girl ratio born but this number appears to level around 1960 and remain constant since then.

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex7.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex7.init.R
# lab1_ex7.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex7.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Keep trying!"
msg3 <- "Awesome, you did great!"
msg4 <- "Try again."
msg5 <- "Try again."

ex() %>% check_mc(3, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

---

## Question 8

```yaml
type: ExplorableExercise
key: ca476ff87f
xp: 50
skills: 1
```

<strong>Follow the directions in the console to open the R Markdown file.</strong>

You can use the RStudio platform just like you would on your home computer.

The markdown file contains the instuctions to answer the multiple choice question below.

<strong>Q8. In what year did we see the most total number of births in the U.S.?</strong>

`@possible_answers`
- 1940
- 1957
- 1961
- 1991
- 2007

`@hint`
Check out the instructions in the .Rmd file to answer the multiple choice question.

`@pre_exercise_code`
```{r}
# Import the helper file contained in the image
source('/usr/local/lib/R/site-library/run_rstudio.R')

# Run a new RStudio session and serve it to the user
run_rstudio()

# .Rprofile: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex8.Rprofile
# .init.R: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex8.init.R
# lab1_ex8.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab1_ex8.Rmd
# lab.css: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab.css
# lab8_wk.RData: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/lab8_wk.RData
```

`@sct`
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Try again."
msg3 <- "Keep trying!"
msg4 <- "Try again."
msg5 <- "Awesome!"

ex() %>% check_mc(5, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
success_msg("Click [here](https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/ch1_key.Rmd) to get a complete Rmarkdown file of the exercises in this Lab and click [here](https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/ch1_key.html) to get the Knitted HTML output.")
```
