---
title       : Insert the chapter title here
description : Insert the chapter description here
attachments :

--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:01bab0ca72

## Generating the pipe operator using keyboard shortcuts2

The keyboard shortcut to generate the pipe operator, %>%, is 'Command + Shift + M' on a Mac or 'Control + Shift + M' on a PC. Open my_code.R, replace the blank space in the script with the pipe operator, and execute the code. What is the output?

*** =instructions

- 1.24328
- 2.33245
- 3.21725
- 3.45543

*** =hint Make sure you've loaded the dplyr package!

*** =pre_exercise_code
```{r,eval=FALSE}

```
*** =sct
```{r,eval=FALSE}
msg1 <- "Awesome!"
msg2 <- "Try again, replace the blank space with the pipe operator using the keyboard shortcut. Execute the code. What is the output?"

test_mc(3, feedback_msgs = c(msg2, msg2, msg1, msg2))
```

*** =attachments
Lab2.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1156/datasets/Lab2.Rmd
