---
title       : Insert the chapter title here
description : Insert the chapter description here
attachments :

--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:02d4222b54
## Lab Question 3
Open the `R Markdown file` that corresponds to this exercise. 

The `file` can be found under `files` tab in the lower right quadrant. The `file` is titled `lab1_ex3.Rmd`. Just click on it and it will open up in the script editor. 

You can use the RStudio platform just like you would on you some computer. Follow the directions and instructions, which, are in the `file` you just opened, however, you can answer the exercise below.

3. Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex3.Rmd
