
title       : Lab 1
description : Insert the chapter description here
attachments :

--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:02d4222b54
##  Question 1
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex1.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

1. How many variables are included in this data set? 

*** =instructions
- 2 
- 3 
- 4
- 82
- 1710
*** =hint
The `dim()` funciton shows the number of rows and columns in a data set.

*** =pre_exercise_code
```{r,eval=FALSE}
# created Lab2.Rmd
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, rerun the `dim()` function on the `arbuthnot` data."
msg2 <- "Nope, what was the result of the `dim()` function."
msg3 <- "Keep trying! Rerun the `dim()` function on the `arbuthnot` data."
msg4 <- "Awesome!"
msg5 <- "Not quite, rerun the `dim()` function on the `arbuthnot` data."

test_mc(4, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```
*** =attachments
lab1_ex1.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex1.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:5440b387f2
## Question 2
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex2.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

2. What command would you use to extract just the counts of girls born? 

*** =instructions
- `arbuthnot$boys`                                                                                    
- `arbuthnot$girls`
- `girls`
- `arbuthnot[girls]` 
- `$girls` 

*** =hint
The `$` operator allows you to call a specific column wihtin a dataset.

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Not quite."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Nope!"
msg5 <- "Try again!"

test_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

*** =attachments
lab1_ex2.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex2.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 3
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex3.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
NEED HINT

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again."
msg5 <- "Try again."

test_mc(2, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```
*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex3.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:e64497e7f4
## Question 4
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex4.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- How many variables are included in this data set?

*** =instructions
- 2
- 3
- 4 
- 74 
- 2013
 

*** =hint
The `dim()` function gives you the number of rows and columns in a data set.

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Try again."
msg3 <- "Keep trying!"
msg4 <- "Awesome!"
msg5 <- "Try again."

test_mc(4, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

*** =attachments
lab1_ex4.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex4.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:b073c8a4d3
## Question 5
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex5.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Has the proportion of boys born in the US has decreased over time.

*** =instructions
- TRUE
- FALSE
 

*** =hint
Use the `range` function and `present$year` as its argument.

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Awesome!"
msg2 <- "Try again."

test_mc(1, feedback_msgs = c(msg1, msg2))
```

*** =attachments
lab1_ex5.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex5.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:8aee5ae535
## Question 6
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex6.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following statements is true?

*** =instructions
- Every year there are more girls born than boys.
- Every year there are more boys born than girls.
- Half of the years there are more boys born, and the other half more girls born. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"

test_mc(2, feedback_msgs = c(msg1, msg2, msg3,))
```

*** =attachments
lab1_ex6.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex6.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:63abfd6950
## Question 7
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex7.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the trend? 

*** =instructions
- There appears to be no trend in the boy-to-girl ratio from 1940 to 2013.
- There is initially an increase in boy-to-girl ratio, which peaks around 1960. After 1960 there is a decrease in the boy-to-girl ratio, but the number begins to increase in the mid 1970s.
- There is initially a decrease in the boy-to-girl ratio, and then an increase between 1960 and 1970, followed by a decrease.
- The boy-to-girl ratio has increased over time.
- There is an initial decrease in the boy-to-girl ratio born but this number appears to level around 1960 and remain constant since then. 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Keep trying!"
msg3 <- "Awesome!"
msg4 <- "Try again."
msg5 <- "Try again."

test_mc(3, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex7.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex7.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:ca476ff87f
## Question 8
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex8.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- In what year did we see the most total number of births in the U.S.?

*** =instructions
- 1940
- 1957   
- 1961        
- 1991
- 2007 
 

*** =hint
Sort your dataset in descending order based on the `total` column. You can do this 
interactively in the data viewer by clicking on the arrows next to the variable 
names. Or to arrange the data in a descenting order with new function: `desc` (for 
descending order).

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again."
msg2 <- "Try again."
msg3 <- "Keep trying!"
msg4 <- "Try again."
msg5 <- "Awesome!"

test_mc(5, feedback_msgs = c(msg1, msg2, msg3, msg4, msg5))
```

*** =attachments
lab1_ex8.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex8.Rmd

