
title       : Lab 1
description : Insert the chapter description here
attachments :

--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:02d4222b54
##  Question 1
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex1.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

1. How many variables are included in this data set? 

*** =instructions
- 2 
- 3 
- 4
- 82
- 1710
*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
# created Lab2.Rmd
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg3 <- "Keep trying!"
msg4 <- "Awesome!"
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(4, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```
*** =attachments
lab1_ex1.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex1.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:5440b387f2
## Question 2
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex2.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

2. What command would you use to extract just the counts of girls born? 

*** =instructions
- `arbuthnot$boys`                                                                                    
- `arbuthnot$girls`
- `girls`
- `arbuthnot[girls]` 
- `$girls` 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex2.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex2.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 3
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex3.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```
*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex3.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 4
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex4.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex4.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 5
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex5.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex5.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 6
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex6.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex6.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 7
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex7.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex7.Rmd


--- type:RStudioMultipleChoiceExercise xp:50 skills:1 key:eb6689ed9c
## Question 8
<strong>Open the `R Markdown file` that corresponds to this exercise.</strong>
<p>The `file` titled `lab1_ex8.Rmd` can be found in the lower right quadrant.</p> 

You can use the RStudio platform just like you would on your home computer. 

<strong>Follow the instructions in the markdown file to answer the multiple choice question below.<strong>

- Which of the following best describes the number of girls baptised over the years included in this dataset?

*** =instructions
- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 
 

*** =hint
Use similar code as the most recent code block above

*** =pre_exercise_code
```{r,eval=FALSE}
```

*** =sct
```{r,eval=FALSE}
msg1 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg2 <- "Awesome!"
msg3 <- "Keep trying!"
msg4 <- "Try again, fill in the code block with the answer using dplyr's `filter`."
msg5 <- "Try again, fill in the code block with the answer using dplyr's `filter`."

test_mc(2, feedback_msgs = c(msg2, msg2, msg1, msg2, msg2))
```

*** =attachments
lab1_ex3.Rmd: https://s3.amazonaws.com/assets.datacamp.com/production/course_1161/datasets/lab1_ex8.Rmd

