---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

Another useful functionality is the ability to quickly calculate summary 
statistics for various groups in your data frame. For example, we can modify the 
above command using the `group_by` function to get the same summary stats for 
each origin airport:

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the # library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)

# The following code is from exercise 1 to create the rdu_flights data frame
rdu_flights <- nycflights %>%
  filter(dest == "RDU")

# The following code is from exercise 1 to create the sfo_feb_flights data frame
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)

```


```{r summary-custom-list-origin}
rdu_flights %>%
  group_by(origin) %>%
  summarise(mean_dd = mean(dep_delay), sd_dd = sd(dep_delay), n = n())
```

Here, we first grouped the data by `origin`, and then calculated the summary 
statistics.

3.  Calculate the median and interquartile range for `arr_delay`s of flights in the 
`sfo_feb_flights` data frame, grouped by carrier. Which carrier is the has the highest 
IQR of arrival delays? 
<strong>Answer Question 3 to the left.</strong>


```{r sfo-feb-flights-arrival-delays-carrier}
# type your code for Question 3 here, and Knit

```

