---  
title: "Introduction to R and RStudio"
output: statsr:::statswithr_lab
---

<div id="exercise">
**Exercise**: What years are included in this dataset? Hint: Take a look at the year 
variable in the Data Viewer to answer this question.
</div>

You should see that the data frame contains the columns `year`,  `boys`, and `girls`. At this point, you might notice that many of the commands in R look a lot like functions from math class; that is, invoking R commands means supplying a function with some number of arguments. The `dim` and `names` commands, for  example, each took a single argument, the name of a data frame.

<div id="boxedtext">
**Tip: ** If you use the up and down arrow keys, you can scroll through your  previous commands, your so-called command history. You can also access it by clicking on the history tab in the upper right panel. This will save you a lot of typing in the future.
</div>

### R Markdown

So far we asked you to type your commands in the console. The console is a great place for playing around with some code, however it is not a good place for  documenting your work. Working in the console exclusively makes it difficult to document your work as you go, and reproduce it later. 

R Markdown is a great solution for this problem. And, you already have worked with an R Markdown document -- this lab! Going forward type the code for the questions in the code chunks provided in the R Markdown (Rmd) document for the lab, and **Knit** the document to see the results.

```{r load-packages, message = FALSE}
# Althought the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(dplyr)
library(statsr)
library(ggplot2)
```

### Some Exploration

Let's start to examine the data a little more closely. We can access the data in a single column of a data frame separately using a command like

```{r view-boys}
arbuthnot$boys
```

This command will only show the number of boys baptized each year. The dollar sign basically says "go to the data frame that comes before me, and find the variable that comes after me".

**See Question 2 to the left.

```{r extract-counts-of-girls-born}
# type your code for the Question 2 here, use the output from this line to answer Question 2, and Knit

```

Notice that the way R has printed these data is different. When we looked at the complete data frame, we saw 82 rows, one on each line of the display. These data are no longer structured in a table with other variables, so they are displayed one right after another. Objects that print out in this way are called vectors; they represent a set of numbers. R has added numbers in [brackets] along the left side of the printout to indicate locations within the vector. For example, 5218 follows [1], indicating that 5218 is the first entry in the vector. And if [43] starts a line, then that would mean the first number on that line would represent the 43rd entry in the vector.

