---
title: "Introduction to R and RStudio"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

## Dataset 2: Present birth records

In the previous few pages, you recreated some of the displays and preliminary analysis of Arbuthnot's baptism data. Next you will do a similar analysis, but for present day birth records in the United States. Load up the present day data with the following command.

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(dplyr)
library(statsr)
library(ggplot2)
```

```{r load-present-data}
data(present)
```

The data are stored in a data frame called `present` which should now be loaded in your workspace.

**See Question 4.

```{r variables-in-present}
# type your code for Question 4 here, use the output from this line to answer Question 4, and Knit

```

<div id="exercise">
**Exercise**: What years are included in this dataset? **Hint:** Use the `range` function and `present$year` as its argument.
</div>

```{r years-in-present-data}
# type your code for Exercise here, and Knit

```

