---
title: "Introduction to R and RStudio"
output: statsr:::statswithr_lab
---

R has some powerful functions for making graphics. We can create a simple plot 
of the number of girls baptized per year with the command

```{r plot-girls-vs-year}

```

Before we review the code for this plot, let's summarize the trends we see in the 
data.

3. Which of the following best describes the number of girls baptised over the years included in this dataset? 

- There appears to be no trend in the number of girls baptised from 1629 to 1710.
- There is initially an increase in the number of girls baptised, which peaks around 1640. After 1640 there is a decrease in the number of girls baptised, but the number begins to increase again in 1660. Overall the trend is an increase in the number of girls baptised. 
- There is initially an increase in the number of girls baptised. This number peaks around 1640 and then after 1640 the number of girls baptised decreases. 
- The number of girls baptised has decreased over time. 
- There is an initial increase in the number of girls baptised but this number appears to level around 1680 and not change after that time point. 


Back to the code... We use the `ggplot()` function to build plots. If you run the 
plotting code in your console, you should see the plot appear under the *Plots* tab 
of the lower right panel of RStudio. Notice that the command above again looks like 
a function, this time with arguments separated by commas. 

- The first argument is always the dataset. 
- Next, we provide thevariables from the dataset to be assigned to `aes`thetic 
elements of the plot, e.g. the x and the y axes. 
- Finally, we use another layer, separated by a `+` to specify the `geom`etric 
object for the plot. Since we want to scatterplot, we use `geom_point`.

You might wonder how you are supposed to know the syntax for the `ggplot` function. 
Thankfully, R documents all of its functions extensively. To read what a function 
does and learn the arguments that are available to you, just type in a question mark 
followed by the name of the function that you're interested in. Try the following in
your console:

```{r plot-help, tidy = FALSE}
?ggplot
```

Notice that the help file replaces the plot in the lower right panel. You can 
toggle between plots and help files using the tabs at the top of that panel. 

More extensive help for plotting with the `ggplot2` package can be found at 
http://docs.ggplot2.org/current/. The best (and easiest) way to learn the syntax is 
to take a look at the sample plots provided on that page, and modify the code 
bit by bit until you get achieve the plot you want.

