---
title: "Introduction to R and RStudio"
output: statsr:::statswithr_lab
---

8. In what year did we see the most total number of births in the U.S.? *Hint:* Sort 
your dataset in descending order based on the `total` column. You can do this 
interactively in the data viewer by clicking on the arrows next to the variable 
names. Or to arrange the data in a descenting order with new function: `desc` (for 
descending order).

```{r load-packages, message = FALSE}
# Althought the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(dplyr)
library(statsr)
library(ggplot2)
```

**See Question 8.

```{r most-total-births}
# type your code for Question 8 here use the output from this line to answer Question 8
# sample code is provided below, edit as necessary, uncomment, and then Knit
#present %>%
#  mutate(total = ?) %>%
#  arrange(desc(total))
```

## Resources for learning R and working in RStudio

That was a short introduction to R and RStudio, but we will provide you with more
functions and a more complete sense of the language as the course progresses. You 
might find the following tips and resources helpful.

- In this course we will be using the `dplyr` (for data wrangling) and `ggplot2` (for 
data visualization) extensively. If you are googling for R code, make sure
to also include these package names in your search query. For example, instead
of googling "scatterplot in R", google "scatterplot in R with ggplot2".

- The following cheathseets may come in handy throughout the course. Note that some 
of the code on these cheatsheets may be too advanced for this course, however 
majority of it will become useful as you progress through the course material.
    - [Data wrangling cheatsheet](http://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf)
    - [Data visualization cheatsheet](http://www.rstudio.com/wp-content/uploads/2015/12/ggplot2-cheatsheet-2.0.pdf)
    - [R Markdown](http://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)

- While you will get plenty of exercise working with these packages in the labs of 
this course, if you would like further opportunities to practice we recommend 
checking out the relevant courses at [DataCamp](https://www.datacamp.com/courses).

<div id="license">
This is a derivative of an [OpenIntro](https://www.openintro.org/stat/labs.php) lab, and is released under a [Attribution-NonCommercial-ShareAlike 3.0 United States](https://creativecommons.org/licenses/by-nc-sa/3.0/us/) license.
</div>
