---
title: "Introduction to R and RStudio"
output: statsr:::statswithr_lab
---

Calculate the total number of births for each year and store these values in a new variable called `total` in the `present` dataset. 

In case you forgot, you can add variables to a dataset using the `$` operator. (i.e. `dataset$new_column <- dataset$column1 -+ dataset$column2`)

Then, calculate the proportion of boys born each year and store these values in a new variable called `prop_boys` in the same dataset. 

Plot these values over time and based on the plot determine if the following statement is true or false: The proportion of boys born in the US has decreased over time. 

You used the following code to plot the proportion of boy births over time for the `arbuthnot` dataset.
`ggplot(data = arbuthnot, aes(x = year, y = boys/total)) + geom_line() + geom_point()`

**See Question 5

```{r load-packages, message = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(dplyr)
library(statsr)
library(ggplot2)
```



```{r prop-boys-over-time}
# type your code for Question 5 here, use the output from this line to answer Question 5, and Knit

```

