---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

5.  Which month has the highest median departure delay from an NYC airport?
<strong>Answer Question 5 to the left.</strong>

Let's think about how we would answer this question:

- In the previous exercise, the monthly averages for departure delays were calculated. For this exercise, we need to
    + `group_by` months, then
    + `summarise` median departure delays.
- Then, we need to `arrange` these average delays in `desc`ending order

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```

```{r mean-dep-delay-months}
# Here is the code from the previous exercise to find the mean departure delay per month
nycflights %>%
  group_by(month) %>%
  summarise(mean_dd = mean(dep_delay)) %>%
  arrange(desc(mean_dd))
```

```{r highest-median-dep-delay-month}
# type your code for Question 5 here, and Knit

```

