---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

6.  Is the mean and the median a more reliable measure for deciding which month(s) to 
avoid flying if you really dislike delayed flights, and why? 
<strong>Answer Question 6 to the left.</strong>


We can also visualize the distributions of departure delays across months using 
side-by-side box plots:

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```


```{r delay-month-box}
ggplot(nycflights, aes(x = factor(month), y = dep_delay)) +
  geom_boxplot()
```

There is some new syntax here: We want departure delays on the y-axis and the
months on the x-axis to produce side-by-side box plots. Side-by-side box plots
require a categorical variable on the x-axis, however in the data frame `month` is 
stored as a numerical variable (numbers 1 - 12). Therefore we can force R to treat
this variable as categorical, what R calls a **factor**, variable with 
`factor(month)`.

