---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

### On time departure rate for NYC airports

Suppose you will be flying out of NYC and want to know which of the 
three major NYC airports has the best on time departure rate of departing flights. 
Suppose also that for you a flight that is delayed for less than 5 minutes is 
basically "on time". You consider any flight delayed for 5 minutes of more to be 
"delayed".

In order to determine which airport has the best on time departure rate, 
we need to 

- first classify each flight as "on time" or "delayed",
- then group flights by origin airport,
- then calculate on time departure rates for each origin airport,
- and finally arrange the airports in descending order for on time departure
percentage.

Let's start with classifying each flight as "on time" or "delayed" by
creating a new variable with the `mutate` function.

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```


```{r dep-type}
nycflights <- nycflights %>%
  mutate(dep_type = ifelse(dep_delay < 5, "on time", "delayed"))
```

The first argument in the `mutate` function is the name of the new variable
we want to create, in this case `dep_type`. Then if `dep_delay < 5` we classify 
the flight as `"on time"` and `"delayed"` if not, i.e. if the flight is delayed 
for 5 or more minutes.

Note that we are also overwriting the `nycflights` data frame with the new 
version of this data frame that includes the new `dep_type` variable.

We can handle all the remaining steps in one code chunk:

```{r}
nycflights %>%
  group_by(origin) %>%
  summarise(ot_dep_rate = sum(dep_type == "on time") / n()) %>%
  arrange(desc(ot_dep_rate))
```

7.  If you were selecting an airport simply based on on time departure percentage, 
which NYC airport would you choose to fly out of? 
<strong>Answer Question 7 to the left.</strong>

```{r on-time-dep-perc-airport}
# type your code for Question 7 here, and Knit

```

We can also visualize the distribution of on on time departure rate across 
the three airports using a segmented bar plot.

```{r}
ggplot(data = nycflights, aes(x = origin, fill = dep_type)) +
  geom_bar()
```
