---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

Some define statistics as the field that focuses on turning information into
knowledge. The first step in that process is to summarize and describe the raw
information - the data. In this lab we explore flights, specifically a random
sample of domestic flights that departed from the three major 
New York City airports in 2013. We will generate simple graphical and numerical 
summaries of data on these flights and explore delay times. As this is a large 
data set, along the way you'll also learn the indispensable skills of data 
processing and subsetting.

## Getting started

### Load packages

In this lab we will explore the data using the `dplyr` package and visualize it 
using the `ggplot2` package for data visualization. The data can be found in the
companion package for this course, `statsr`.

Let's load the packages.

```{r load-packages, message=FALSE}
library(statsr)
library(dplyr)
library(ggplot2)
```

### Data

The [Bureau of Transportation Statistics](http://www.rita.dot.gov/bts/about/) 
(BTS) is a statistical agency that is a part of the Research and Innovative 
Technology Administration (RITA). As its name implies, BTS collects and makes 
available transportation data, such as the flights data we will be working with 
in this lab.

We begin by loading the `nycflights` data frame. Type the following in your console
to load the data:

```{r load-data}
data(nycflights)
```

The data frame containing `r nrow(nycflights)` flights that shows up in your 
workspace is a *data matrix*, with each row representing an *observation* and each 
column representing a *variable*. R calls this data format a **data frame**, which is 
a term that will be used throughout the labs.

To view the names of the variables, type the command

```{r names}
names(nycflights)
```

This returns the names of the variables in this data frame. The **codebook**
(description of the variables) is included below. This information can also be
found in the help file for the data frame which can be accessed by typing
`?nycflights` in the console.

- `year`, `month`, `day`: Date of departure
- `dep_time`, `arr_time`: Departure and arrival times, local timezone.
- `dep_delay`, `arr_delay`: Departure and arrival delays, in minutes. Negative times represent early departures/arrivals.
- `carrier`: Two letter carrier abbreviation.
    + `9E`:           Endeavor Air Inc.
    + `AA`:      American Airlines Inc.
    + `AS`:        Alaska Airlines Inc.
    + `B6`:             JetBlue Airways
    + `DL`:        Delta Air Lines Inc.
    + `EV`:    ExpressJet Airlines Inc.
    + `F9`:      Frontier Airlines Inc.
    + `FL`: AirTran Airways Corporation
    + `HA`:      Hawaiian Airlines Inc.
    + `MQ`:                   Envoy Air
    + `OO`:       SkyWest Airlines Inc.
    + `UA`:       United Air Lines Inc.
    + `US`:             US Airways Inc.
    + `VX`:              Virgin America
    + `WN`:      Southwest Airlines Co.
    + `YV`:          Mesa Airlines Inc.
- `tailnum`: Plane tail number
- `flight`: Flight number
- `origin`, `dest`: Airport codes for origin and destination. (Google can help
you with what code stands for which airport.)
- `air_time`: Amount of time spent in the air, in minutes.
- `distance`: Distance flown, in miles.
- `hour`, `minute`: Time of departure broken in to hour and minutes.

A very useful function for taking a quick peek at your data frame, and viewing
its dimensions and data types is `str`, which stands for **str**ucture.

```{r str}
str(nycflights)
```

The `nycflights` data frame is a massive trove of information. Let's think about 
some questions we might want to answer with these data:

- We might want to find out how delayed flights headed to a particular 
destination tend to be. 
- We might want to evaluate how departure delays vary over months. 
- Or we might want to determine which of the three major NYC airports has a better 
on-time percentage for departing flights.

### Seven verbs

The `dplyr` package offers seven verbs (functions) for basic data 
manipulation:

- `filter()`
- `arrange()`
- `select()` 
- `distinct()`
- `mutate()`
- `summarise()`
- `sample_n()`

We will use some of these functions in this lab, and learn about others in a 
future lab.


## Analysis

### Departure delays in flights to Raleigh-Durham (RDU)

We can examine the distribution of departure delays of all flights with a 
histogram.

```{r hist-dep-delay}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram()
```

This function says to plot the `dep_delay` variable from the `nycflights` data 
frame on the x-axis. It also defines a `geom` (short for geometric object), 
which describes the type of plot you will produce. 

Histograms are generally a very good way to see the shape of a single 
distribution, but that shape can change depending on how the data is split 
between the different bins. You can easily define the binwidth you want to use:

```{r hist-dep-delay-bins}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 15)
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 150)
```

<div id="exercise">
**Exercise**: How do these three histograms with the various binwidths compare?
</div>

If we want to focus on departure delays of flights headed to RDU only, we need to
first `filter` the data for flights headed to RDU (`dest == "RDU"`) and then make
a histogram of only departure delays of only those flights.

```{r rdu-flights-hist}
rdu_flights <- nycflights %>%
  filter(dest == "RDU")
ggplot(data = rdu_flights, aes(x = dep_delay)) +
  geom_histogram()
```

Let's decipher these three lines of code:

- Line 1: Take the `nycflights` data frame, `filter` for flights headed to RDU, and 
save the result as a new data frame called `rdu_flights`.
    + `==` means "if it's equal to".
    + `RDU` is in quotation marks since it is a character string.
- Line 2: Basically the same `ggplot` call from earlier for making a histogram, 
except that it uses the data frame for flights headed to RDU instead of all
flights.

<div id="boxedtext">
**Logical operators: ** Filtering for certain observations (e.g. flights from a 
particular airport) is often of interest in data frames where we might want to 
examine observations with certain characteristics separately from the rest of 
the data. To do so we use the `filter` function and a series of 
**logical operators**. The most commonly used logical operators for data 
analysis are as follows:

- `==` means "equal to"
- `!=` means "not equal to"
- `>` or `<` means "greater than" or "less than"
- `>=` or `<=` means "greater than or equal to" or "less than or equal to"
</div>

We can also obtain numerical summaries for these flights:

```{r rdu-flights-summ}
rdu_flights %>%
  summarise(mean_dd = mean(dep_delay), sd_dd = sd(dep_delay), n = n())
```

Note that in the `summarise` function we created a list of two elements. The 
names of these elements are user defined, like `mean_dd`, `sd_dd`, `n`, and 
you could customize these names as you like (just don't use spaces in your 
names). Calculating these summary statistics also require that you know the 
function calls. Note that `n()` reports the sample size.

<div id="boxedtext">
**Summary statistics: ** Some useful function calls for summary statistics for a 
single numerical variable are as follows:

- `mean`
- `median`
- `sd`
- `var`
- `IQR`
- `range`
- `min`
- `max`
</div>

We can also filter based on multiple criteria. Suppose we are interested in
flights headed to San Francisco (SFO) in February:

```{r}
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)
```

Note that we can separate the conditions using commas if we want flights that
are both headed to SFO **and** in February. If we are interested in either
flights headed to SFO **or** in February we can use the `|` instead of the comma.

1. Create a new data frame that includes flights headed to SFO in February, and save 
this data frame as `sfo_feb_flights`. How many flights meet these criteria? 
<strong>Answer Question 1 to the left.</strong>

```{r sfo-feb-flights}
# type your code for Question 1 here, and Knit

```
