---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---


```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)

# The following code is from exercise 1 to create the sfo_feb_flights data frame
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)

# The following code is from exercise 1 to create the rdu_flights data frame
rdu_flights  <- nycflights %>%
  filter(dest == "RDU") 

# The following code is from exercise 1 to create the a plot with the rdu_flights data frame
ggplot(data = rdu_flights, aes(x = dep_delay)) +
  geom_histogram()

# The following code is from exercise 1 to summarize the rdu_flights data frame
rdu_flights  %>%
  summarise(mean_dd = mean(dep_delay), sd_dd = sd(dep_delay), n = n())

```
Note that in the `summarise` function we created a list of two elements. The 
names of these elements are user defined, like `mean_dd`, `sd_dd`, `n`, and 
you could customize these names as you like (just don't use spaces in your 
names). Calculating these summary statistics also require that you know the 
function calls. Note that `n()` reports the sample size.

<div id="boxedtext">
**Summary statistics: ** Some useful function calls for summary statistics for a 
single numerical variable are as follows:

- `mean`
- `median`
- `sd`
- `var`
- `IQR`
- `range`
- `min`
- `max`
</div>

2. Make a histogram and calculate appropriate summary statistics for **arrival** 
delays of `sfo_feb_flights`. Which of the following is false? 
<strong>Answer Question 2 to the left.</strong>

```{r sfo-feb-flights-arrival-delays}
# type your code for Question 2 here, and Knit

```

