---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

### Departure delays over months

Which month would you expect to have the highest average delay departing 
from an NYC airport?

Let's think about how we would answer this question:

- First, calculate monthly averages for departure delays. With the new language
we are learning, we need to
    + `group_by` months, then
    + `summarise` mean departure delays.
- Then, we need to `arrange` these average delays in `desc`ending order

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```
ddd

```{r mean-dep-delay-months}
nycflights %>%
  group_by(month) %>%
  summarise(mean_dd = mean(dep_delay)) %>%
  arrange(desc(mean_dd))
```

4.  Which month has the highest average departure delay from an NYC airport? 
<ol>
<li> January </li> 
<li> March </li> 
<li> July </li> 
<li> October </li>
<li> December </li>
</ol>

```{r highest-avg-dep-delay-month}
# type your code for Question 4 here, and Knit

```

