---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

8.  Mutate the data frame so that it includes a new variable that contains the 
average speed, `avg_speed` traveled by the plane for each flight (in mph). What is 
the tail number of the plane with the fastest `avg_speed`? **Hint:** Average speed 
can be calculated as distance divided by number of hours of travel, and note that 
`air_time` is given in minutes. If you just want to show the `avg_speed` and 
`tailnum` and none of the other variables, use the select function at the end of your 
pipe to select just these two variables with `select(avg_speed, tailnum)`. You can 
Google this tail number to find out more about the aircraft. 
<ol>
<li> N666DN </li> 
<li> N755US </li> 
<li> N779JB </li> 
<li> N947UW </li> 
<li> N959UW </li> 
</ol>

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```


```{r fastest-avg-speed-tailnum}
# type your code for Question 8 here, and Knit

```
