---
title: "Probability"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---
Counting streak lengths manually for all 133 shots would get tedious, so we'll
use the custom function `calc_streak` to calculate them, and store the results
in a data frame called `kobe_streak` as the `length` variable.

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```

```{r calc-streak-kobe}
kobe_streak <- calc_streak(kobe_basket$shot)
```

We can then take a look at the distribution of these streak lengths.

```{r plot-streak-kobe}
ggplot(data = kobe_streak, aes(x = length)) +
  geom_histogram(binwidth = 1)
```

3.  Which of the following is false about the distribution of Kobe's streak lengths 
from the 2009 NBA finals. 
<strong> Answer Question 1 to the left.</strong>

