---
title: "Introduction to R and RStudio"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

The goal of this lab is to introduce you to R and RStudio, which you'll be using throughout the course both to learn the statistical concepts discussed in the  course and to analyze real data and come to informed conclusions. To straighten  out which is which: R is the name of the programming language itself and RStudio is a convenient interface.

As the labs progress, you are encouraged to explore beyond what the labs dictate; a willingness to experiment will make you a much better programmer. Before we get to that stage, however, you need to build some basic fluency in R. Today we begin with the fundamental building blocks of R and RStudio: the interface, reading in data, and basic commands.

## RStudio

Your RStudio window has four panels.

Your R Markdown file (this document) is in the upper left panel.

The panel on the lower left is where the action happens. It's called the *console*. Every time you launch RStudio, it will have the same text at the top of the console telling you the version of R that you're running. Below that information is the *prompt*. As its name suggests, this prompt is really a request, a  request for a command. Initially, interacting with R is all about typing commands and interpreting the output. These commands and their syntax have evolved over decades (literally) and now provide what many users feel is a fairly natural way to access data and organize, describe, and invoke statistical computations.

The panel in the upper right contains your *workspace* as well as a history of the commands that you've previously entered. 

Any plots that you generate will show up in the panel in the lower right corner. This is also where you can browse your files, access help, manage packages, etc.


## R Packages

R is an open-source programming language, meaning that users can contribute packages that make our lives easier, and we can use them for free. For this lab, and many others in the future, we will use the following R packages:

- `statsr`: for data files and functions used in this course
- `dplyr`: for data wrangling
- `ggplot2`: for data visualization

You should have already installed these packages using commands like  `install.packages` and `install_github`.

Next, you need to load the packages in your working environment. We do this with the `library` function. Note that you only need to **install** packages once, but you need to 
**load** them each time you relaunch RStudio.
```{r load-packages, message = FALSE}
library(dplyr)
library(ggplot2)
library(statsr)

```

To do so, you can 

- click on the green arrow at the top of the code chunk in the R Markdown (Rmd) file, or
- highlight these lines, and hit the **Run** button on the upper right corner of the pane, or
- type the code in the console.

Going forward you will be asked to load any relevant packages at the beginning of each lab.

## Dataset 1: Example Data set

To get you started, we will run an example dataset to show some of the functionality of RStudio and R Markdown.

```{r load-cars-data}
data(cars)
```

To do so, once again, you can 

- click on the green arrow at the top of the code chunk in the R Markdown (Rmd)  file, or
- put your cursor on this line, and hit the **Run** button on the upper right  corner of the pane, or
- type the code in the console.

This command instructs R to load some data. The `cars` dataset is a list of speeds and stopping distances of cars. You should see that the workspace area in the upper righthand corner of the RStudio window now lists a data set called `cars` that has 50 observations on 2 variables. As you interact with R, you will create a series of objects. Sometimes you load them as we have done here, and sometimes you create them yourself  as the byproduct of a computation or some analysis you have performed.

The `cars` dataset is a stored dataset within the base packages in R.

```{r view-data}
cars
```

However printing the whole dataset in the console is not that useful.  One advantage of RStudio is that it comes with a built-in data viewer. Click on the name `cars` in the *Environment* pane (upper right window) that lists the objects in your workspace. This will bring up an alternative display of the  data set in the *Data Viewer* (upper left window). You can close the data viewer by clicking on the *x* in the upper lefthand corner.

What you should see are four columns of numbers, each row representing a different car: the first entry in each row is simply the row number, the second is the speed, and the third is the distnace it took to stop. Use the scrollbar on the right side of the console window to examine the complete data set.

Note that the row numbers in the first column are not part of `cars's` data. R adds them as part of its printout to help you make visual comparisons. You can think of them as the index that you see on the left side of a spreadsheet. In fact, the comparison to a spreadsheet will generally be helpful. R has stored `cars's` data in a kind of spreadsheet or table called a *data frame*.

You can see the dimensions of this data frame by typing:

```{r dim-data}
# use the output from this line to answer Question 1, and Knit
dim(cars)
```

This command should output `[1] 50 2`, indicating that there are 50 rows and 2 columns (we'll get to what the `[1]` means in a bit), just as it says next to the object in your workspace. You can see the names of these columns (or variables) by typing:

```{r names-data}
names(cars)
```

1. How many variables are included in this data set? <strong>Answer Question 1 to the left.</strong>


<div id="exercise">
**Exercise**: What is the longest stopping distance included in this dataset? Hint: Take a look at the `dist` variable in the Data Viewer to answer this question.
</div>

You should see that the data frame contains the columns `distance`, and `speed`. At this point, you might notice that many of the commands in R look a lot like functions from math class; that is, invoking R commands means supplying a function with some number of arguments. The `dim` and `names` commands, for  example, each took a single argument, the name of a data frame.

<div id="boxedtext">
**Tip: ** If you use the up and down arrow keys, you can scroll through your  previous commands, your so-called command history. You can also access it by clicking on the history tab in the upper right panel. This will save you a lot of typing in the future.
</div>

### R Markdown

So far we asked you to type your commands in the console. The console is a great place for playing around with some code, however it is not a good place for  documenting your work. Working in the console exclusively makes it difficult to document your work as you go, and reproduce it later. 

R Markdown is a great solution for this problem. And, you already have worked with an R Markdown document -- this lab! Going forward type the code for the questions in the code chunks provided in the R Markdown (Rmd) document for the lab, and **Knit** the document to see the results.

### Some Exploration

Let's start to examine the data a little more closely. We can access the data in a single column of a data frame separately using a command like

```{r view-speed}
data(cars)
cars$speed
```

This command will only show the average spped for the list of trips in the dataset. The dollar sign basically says "go to the data frame that comes before me, and find the variable that comes after me".

2. What command would you use to extract just the longest stopping distance? <strong>Answer Question 2 to the left.</strong>

```{r fastest-speed}
# type your code for the Question 2 here, use the output from this line to answer Question 2, and Knit
cars$dist
```

Notice that the way R has printed these data is different. When we looked at the complete data frame, we saw 50 rows, one on each line of the display. These data are no longer structured in a table with other variables, so they are displayed one right after another. Objects that print out in this way are called vectors; they represent a set of numbers. R has added numbers in [brackets] along the left side of the printout to indicate locations within the vector. For example, 5218 follows [1], indicating that 5218 is the first entry in the vector. And if [43] starts a line, then that would mean the first number on that line would represent the 43rd entry in the vector.

