---
title: "Introduction to R and RStudio"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

The goal of this lab is to introduce you to R and RStudio, which you'll be using throughout the course both to learn the statistical concepts discussed in the  course and to analyze real data and come to informed conclusions. To straighten  out which is which: R is the name of the programming language itself and RStudio is a convenient interface.

As the labs progress, you are encouraged to explore beyond what the labs dictate; a willingness to experiment will make you a much better programmer. Before we get to that stage, however, you need to build some basic fluency in R. Today we begin with the fundamental building blocks of R and RStudio: the interface, reading in data, and basic commands.

## RStudio

Your RStudio window has four panels.

Your R Markdown file (this document) is in the upper left panel.

The panel on the lower left is where the action happens. It's called the *console*. Every time you launch RStudio, it will have the same text at the top of the console telling you the version of R that you're running. Below that information is the *prompt*. As its name suggests, this prompt is really a request, a  request for a command. Initially, interacting with R is all about typing commands and interpreting the output. These commands and their syntax have evolved over decades (literally) and now provide what many users feel is a fairly natural way to access data and organize, describe, and invoke statistical computations.

The panel in the upper right contains your *workspace* as well as a history of the commands that you've previously entered. 

Any plots that you generate will show up in the panel in the lower right corner. This is also where you can browse your files, access help, manage packages, etc.


## R Packages

R is an open-source programming language, meaning that users can contribute packages that make our lives easier, and we can use them for free. For this lab, and many others in the future, we will use the following R packages:

- `statsr`: for data files and functions used in this course
- `dplyr`: for data wrangling
- `ggplot2`: for data visualization

You should have already installed these packages using commands like  `install.packages` and `install_github`.

Next, you need to load the packages in your working environment. We do this with the `library` function. Note that you only need to **install** packages once, but you need to 
**load** them each time you relaunch RStudio.
```{r load-packages, message = FALSE}
library(dplyr)
library(ggplot2)
library(statsr)

```

To do so, you can 

- click on the green arrow at the top of the code chunk in the R Markdown (Rmd) file, or
- highlight these lines, and hit the **Run** button on the upper right corner of the pane, or
- type the code in the console.

Going forward you will be asked to load any relevant packages at the beginning of each lab.

## Dataset 1: Dr. Arbuthnot's Baptism Records

To get you started, run the following command to load the data.

```{r load-abrbuthnot-data}
data(arbuthnot)
```

To do so, once again, you can 

- click on the green arrow at the top of the code chunk in the R Markdown (Rmd)  file, or
- put your cursor on this line, and hit the **Run** button on the upper right  corner of the pane, or
- type the code in the console.

This command instructs R to load some data. The Arbuthnot baptism counts for boys and girls. You should see that the workspace area in the upper righthand corner of the RStudio window now lists a data set called `arbuthnot` that has 82 observations on 3 variables. As you interact with R, you will create a series of objects. Sometimes you load them as we have done here, and sometimes you create them yourself  as the byproduct of a computation or some analysis you have performed.

The Arbuthnot data set refers to Dr. John Arbuthnot, an 18<sup>th</sup> century physician, writer, and mathematician. He was interested in the ratio of newborn boys to newborn girls, so he gathered the baptism records for children born in London for every year from 1629 to 1710. We can take a look at the data by  typing its name into the console.

```{r view-data}
arbuthnot
```

However printing the whole dataset in the console is not that useful.  One advantage of RStudio is that it comes with a built-in data viewer. Click on the name `arbuthnot` in the *Environment* pane (upper right window) that lists the objects in your workspace. This will bring up an alternative display of the  data set in the *Data Viewer* (upper left window). You can close the data viewer by clicking on the *x* in the upper lefthand corner.

What you should see are four columns of numbers, each row representing a  different year: the first entry in each row is simply the row number (an index we can use to access the data from individual years if we want), the second is the year, and the third and fourth are the numbers of boys and girls baptized that year, respectively. Use the scrollbar on the right side of the console window to examine the complete data set.

Note that the row numbers in the first column are not part of Arbuthnot's data. R adds them as part of its printout to help you make visual comparisons. You can think of them as the index that you see on the left side of a spreadsheet. In fact, the comparison to a spreadsheet will generally be helpful. R has stored Arbuthnot's data in a kind of spreadsheet or table called a *data frame*.

You can see the dimensions of this data frame by typing:

```{r dim-data}
# use the output from this line to answer Question 1, and Knit
dim(arbuthnot)
```

This command should output `[1] 82 3`, indicating that there are 82 rows and 3 columns (we'll get to what the `[1]` means in a bit), just as it says next to the object in your workspace. You can see the names of these columns (or variables) by typing:

```{r names-data}
names(arbuthnot)
```

1. How many variables are included in this data set? <strong>Answer Question 1 to the left.</strong>
