---
title: "Introduction to data"
output:
  html_document: 
    theme: cerulean 
    highlight: pygments
    css: lab.css
---

10.  Suppose you define a flight to be "on time" if it gets to the destination on time or earlier than expected, regardless of any departure delays. Mutate the data frame to create a new variable called `arr_type` with levels `"on time"` and `"delayed"` based on this definition. Also mutate to create a new variable called `dep_type` with levels `"on time"` and `"delayed"` depending on the flight was delayed for fewer than 5 minutes or 5 minutes or more, respectively. In other words, if `arr_delay` is 0 minutes or fewer, `arr_type` is `"on time"`. If `dep_delay` is less than 5 minutes, `dep_type` is `"on time"`. Then, determine the on time arrival percentage based on whether the flight departed on time or not. What percent of flights that were `"delayed"` departing arrive `"on time"`?
<strong>Answer Question 10 to the left.</strong>

```{r load-packages, message = FALSE, echo = FALSE}
# Although the packages ggplot2, dplyr, and statsr are loaded, to Knit, you must have the library functions in your .Rmd file. Don't erase this code block!
library(statsr)
library(dplyr)
library(ggplot2)
```


```{r on-time-arr-perc}
# type your code for Question 10 here, and Knit

```
